Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-26 manuscript.Rmd
Reformatting journal.

---
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
date: "May 26, 2015"
output: pdf_document
---

@@

```{r plotAuthorCount, eval=TRUE, cache=FALSE}
year.df <- full.df %>%
    filter(attributes == "pubYear") %>%
    select(id = articleID, pubYear = record)

@@

```{r pagePlot, eval=TRUE, cache=FALSE}
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages), years = as.numeric(years)) %>%
    group_by(years) %>%
    summarise(
        Median = median(pages, na.rm=TRUE), 
        Average = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))

@@

```{r plotStacked, cache=FALSE}
abstract.df <- filter(full.df, attributes == "abstract")
year.df <- filter(full.df, attributes == "pubYear")
journal.df <- filter(full.df, attributes == "journal")
abstract.df <- left_join(year.df, abstract.df, by = "articleID")
abstract.df <- left_join(abstract.df, journal.df, by = "articleID")
abstract.df <- abstract.df %>% select(-attributes.x, -attributes.y, -attributes)
colnames(abstract.df) <- c("articleID", "year", "abstract", "journal")
abstract.df$abstract <- gsub("[[:punct:]]", "", abstract.df$abstract)
abstract.df$abstract <- tolower(abstract.df$abstract)

@@

evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis,\nSys Rev", "Quasi-experimental", "RCT"))

@@

```{r plotProportions, cache=FALSE}
df <- evidence.summary2

@@

```{r plotClevelandAbsolute}
evidence.summary3 <- select(evidence.df, -abstract) %>% 
    group_by(journal, studyType) %>%
    summarize(N = n())

@@

```{r plotEBPstackedBar}

@@

```{r plotEBPproportion}

@@

options(digits=3)
proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
    theme_bw() + 
    geom_point(colour="grey40") +
    geom_segment(aes(yend = Abbrev, xend = 0), colour = "grey40") + 
    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
          legend.position = "none", 
          panel.grid.minor = element_blank(), 
            panel.margin = unit(0,"null")) + 
    ylab(NULL) +
    xlab("Proportion") +
    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 2.5) +
    xlim(c(0, .5))  +
    theme(axis.text.x = element_text(size=8),  
    title = element_text(size = 8), plot.title=element_text(size=8)) +
    theme(legend.text = element_text(size = 8))

>>>>

---
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
date: "May 26, 2015"
output: pdf_document
header-includes:
- \usepackage{indentfirst}
- \usepackage{setspace}
- \doublespacing
- \setlength{\parindent}{4em}
---

@@

```{r plot03_AuthorPages, eval=TRUE, cache=FALSE}

#----------------------------
#Authors
#----------------------------

year.df <- full.df %>%
    filter(attributes == "pubYear") %>%
    select(id = articleID, pubYear = record)

@@

#----------------------------
#Pages
#----------------------------

cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages), years = as.numeric(years)) %>%
    group_by(years) %>%
    summarise(
        Median = median(pages, na.rm=TRUE), 
        Average = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))

@@

```{r plot04_EBPstacked, cache=FALSE}
abstract.df <- filter(full.df, attributes == "abstract")
year.df <- filter(full.df, attributes == "pubYear")
journal.df <- filter(full.df, attributes == "journal")
abstract.df <- left_join(year.df, abstract.df, by = "articleID")
abstract.df <- left_join(abstract.df, journal.df, by = "articleID")
abstract.df <- abstract.df %>% select(-attributes.x, -attributes.y, -attributes)
colnames(abstract.df) <- c("articleID", "year", "abstract", "journal")
abstract.df$abstract <- gsub("[[:punct:]]", "", abstract.df$abstract)
abstract.df$abstract <- tolower(abstract.df$abstract)

@@

evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis,\nSystematic Review", "Quasi-experimental", "RCT"))

@@

```{r plot05_ProportionsLine, cache=FALSE}
df <- evidence.summary2

@@

```{r plot06_EBPjournal, cache=FALSE}
evidence.summary3 <- select(evidence.df, -abstract) %>% 
    group_by(journal, studyType) %>%
    summarize(N = n())

@@

@@

```{r plot07_EBPproportion, cache=FALSE}

@@

options(digits=3)
proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
    theme_bw() + 
    geom_point(colour="grey40") +
    geom_segment(aes(yend = Abbrev, xend = 0), colour = "grey40") + 
    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
          legend.position = "none", 
          panel.grid.minor = element_blank(), 
            panel.margin = unit(0,"null")) + 
    ylab(NULL) +
    xlab("Proportion") +
    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 2.5) +
    xlim(c(0, .5))  +
    theme(axis.text.x = element_text(size=8),  
    title = element_text(size = 8), plot.title=element_text(size=8)) +
    theme(legend.text = element_text(size = 8))
```
